---
title: "History of Amherst College data package"
author: "STAT325 class at Amherst College (Nicholas Horton)"
date: "2024-04-03"
date-format: iso
format: gfm
editor: source
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(HistoryAmherstCollege)
```

## Text and analysis related to Williams S. Tyler's "History of Amherst College" (1873)

This repo provides the curated text from the book entitled *History of Amherst College during the First Half Century*.

See https://archive.org/details/historyofamherst00tyleiala for the book in a variety of formats.

Our mission was to take the text file for this historic text and make it accessible more broadly.

This file describes the `HistoryAmherstCollege` package.

## Website

A website can be found at https://stat325-s24.github.io/HistoryAmherstCollege/

## Installation instructions

```
devtools::install_github("STAT325-S24/HistoryAmherstCollege")
library(HistoryAmherstCollege)
```

## Example analyses

XX will go here...

```{r}
glimpse(history_text)
glimpse(history_anno)
```


## Notes

- The index was not included in the text in the package
- Footnotes were moved into the text where referenced (e.g., `[This is a footnote.]`)
- Erratum on page 671 states: `On page 290, line 20, for Humphrey read Hitchcock`. This change has been noted in the text.
