---
title: "Example Analysis"
page-layout: full
title-block-banner: true
---



```{r, include = FALSE}
library(dplyr)
#devtools::install_github("STAT325-S24/HistoryAmherstCollege")
library(HistoryAmherstCollege)
```



## Example analyses

The following is a glimpse of the package's dataframes along with a sample analysis using Named Entity Recognition (thanks to the `cleanNLP` package).

```{r}
packageVersion("HistoryAmherstCollege")
glimpse(history_text)
mosaic::tally(~ chapter, data = history_text)
glimpse(history_anno)
mosaic::tally(~ entity$entity_type, data = history_anno)
glimpse(history_subtitles)
glimpse(history_tables)
glimpse(history_figures)
```

```{r}
history_anno$entity |>
  filter(entity_type == "PERSON") |>
  group_by(entity) |>
  count() |>
  arrange(desc(n)) |>
  head(6)
```

The above table shows us the 6 most common names in the book.
Some familiar ones immediately pop out, such as Hitchcock, the eponym of the "Hitchcock Residence Hall" and one of the founding members of the American Statistical Association.

```{r}
history_anno$token |>
  filter(upos == "NOUN") |>
  group_by(token) |>
  count() |>
  arrange(desc(n)) |>
  head(6)
```

The above table displays the 6 most common nouns in the text.
Unsurprisingly, we see "students" as the most common noun.

